Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2020-11-27 manuscript.tex
Link to national legislation [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/76040d57b99841c6ef4f59363df8779f86b9ddad.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/76040d57b99841c6ef4f59363df8779f86b9ddad/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/387193518

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...877b421bd54e45c8867c3532d8125a141e25bf7d}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/877b421bd54e45c8867c3532d8125a141e25bf7d/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/877b421bd54e45c8867c3532d8125a141e25bf7d}{habi/zmk-tooth-cohort-method-manuscript@877b421}
on November 10, 2020.

@@

The 104 human permanent mandibular canines in this study were collected from university medical centers in southwest Germany and Switzerland.
All included teeth were extracted for reasons unrelated to the study and are so-called excess material.
This makes an ethics approval unnecessary for the purpose of this investigation, as well as consent to participate and for publication.

@@

\leavevmode\hypertarget{ref-19SVNdOdA}{}%
13. Wolf TG, Kozaczek C, Campus G, Paqué F, Wierichs RJ. Root canal morphology of 116 maxillary second premolars by micro-CT in a mixed Swiss-German population with systematic review. Journal of Endodontics. 2020. doi:\href{https://doi.org/10.1016/j.joen.2020.08.012}{10.1016/j.joen.2020.08.012}.

@@

\leavevmode\hypertarget{ref-8Miti2Gz}{}%
27. Virtanen P, Gommers R, Oliphant TE, Haberland M, Reddy T, Cournapeau D, et al. SciPy 1.0: fundamental algorithms for scientific computing in Python. Nature Methods. 2020. doi:\href{https://doi.org/10.1038/s41592-019-0686-2}{10.1038/s41592-019-0686-2}.

@@

\leavevmode\hypertarget{ref-Q20Bxdsr}{}%
36. Jupyter P, Bussonnier M, Forde J, Freeman J, Granger B, Head T, et al. Binder 2.0 - Reproducible, interactive, sharable environments for science at scale. SciPy. 2018. doi:\href{https://doi.org/10.25080/majora-4af1f417-011}{10.25080/majora-4af1f417-011}.
\end{cslreferences}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...76040d57b99841c6ef4f59363df8779f86b9ddad}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/76040d57b99841c6ef4f59363df8779f86b9ddad/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/76040d57b99841c6ef4f59363df8779f86b9ddad}{habi/zmk-tooth-cohort-method-manuscript@76040d5}
on November 27, 2020.

@@

The 104 human permanent mandibular canines in this study were collected from university medical centers in southwest Germany and Switzerland.
All included teeth were extracted for reasons unrelated to the study and are so-called excess material.
The teeth were used under irreversibly anonymized conditions and in accordance with the Swiss Human Research Law (\emph{Humanforschungsgesetz} {[}\protect\hyperlink{ref-4nfESi56}{37}{]}).
All donors were adults and gave written informed consent for research purposes.
This makes an ethics approval unnecessary for the purpose of this investigation.

@@

\leavevmode\hypertarget{ref-19SVNdOdA}{}%
13. Wolf TG, Kozaczek C, Campus G, Paqué F, Wierichs RJ. Root Canal Morphology of 116 Maxillary Second Premolars by Micro--Computed Tomography in a Mixed Swiss-German Population with Systematic Review. Journal of Endodontics. 2020;46:1639--47. doi:\href{https://doi.org/10.1016/j.joen.2020.08.012}{10.1016/j.joen.2020.08.012}.

@@

\leavevmode\hypertarget{ref-8Miti2Gz}{}%
27. Virtanen P, Gommers R, Oliphant TE, Haberland M, Reddy T, Cournapeau D, et al. SciPy 1.0: fundamental algorithms for scientific computing in Python. Nature Methods. 2020;17:261--72. doi:\href{https://doi.org/10.1038/s41592-019-0686-2}{10.1038/s41592-019-0686-2}.

@@

\leavevmode\hypertarget{ref-Q20Bxdsr}{}%
36. Jupyter P, Bussonnier M, Forde J, Freeman J, Granger B, Head T, et al. Binder 2.0 - Reproducible, interactive, sharable environments for science at scale. SciPy. 2018. doi:\href{https://doi.org/10.25080/majora-4af1f417-011}{10.25080/majora-4af1f417-011}.

\leavevmode\hypertarget{ref-4nfESi56}{}%
37. SR 810.30 Bundesgesetz vom 30. September 2011 über die Forschung am Menschen (Humanforschungsgesetz, HFG). \url{https://www.admin.ch/opc/de/classified-compilation/20061313/index.html}. Accessed 27 Nov 2020.
\end{cslreferences}
